### 2018-05-24 Main.Rmd

List of libraries
```{r}
  library(purrr)
  library(readr)
  library(ggplot2)
  library(langcog)
  library(boot)
  library(dplyr)
  library(tidyr)
  library(wordbankr)
  library(directlabels)
  library(stringr)
  library(lmtest)
  library(rwebppl)
  library(jsonlite)
  library(nlme)
  library(feather)
  library(broom)
  library(HDInterval)
  library(BBmisc)
  library(igraph)
```

Import helper functions

```{r}
source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
```

Create pairs

```{r}
#Import data from wordbank in a format that will be useful for us (especially when we will do development in time).

@@

Build graphs

```{r}
assoc_links <- assoc_pairs %>%
  filter(link==1) %>%
  select(item, pair, item.definition, pair.definition)

@@

assoc_graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>%
  simplify()

feature_graph <- graph_from_data_frame(feature_links, directed=FALSE, vertices=lemma_list) %>%
  simplify()

print(assoc_graph, e=TRUE, v=TRUE)
print(feature_graph, e=TRUE, v=TRUE)
```

>>>>

---
output:
  html_document: default
  pdf_document: default
---
# Basic Network Analysis of Wordbank Data

## Build Networks

List of libraries
```{r echo=TRUE, warning=FALSE, message=FALSE}
library(purrr)
library(readr)
library(ggplot2)
library(langcog)
library(boot)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
library(stringr)
library(lmtest)
library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
library(igraph)
library(knitr)
library(lemon)
library(tibble)
```

Import helper functions and configure RMarkdown
```{r echo=TRUE, warning=FALSE, message=FALSE}
source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

knit_print.data.frame <- lemon_print # use kable when displaying tibbles in knit
```

Create pairs 
```{r echo=TRUE, warning=FALSE, message=FALSE}
#Import data from wordbank in a format that will be useful for us (especially when we will do development in time).

@@

Build networks
```{r}
assoc_links <- assoc_pairs %>%
  filter(link==1) %>%
  select(item, pair, item.definition, pair.definition)

@@

assoc_network <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>%
  simplify() %>%
  set.graph.attribute("name", "Assoc") # maybe rewrite as g$name <- "Name"

feature_network <- graph_from_data_frame(feature_links, directed=FALSE, vertices=lemma_list) %>%
  simplify() %>%
  set.graph.attribute("name", "Feature")

networks <- list(assoc_network, feature_network)
```

## Network Analysis

### Large-Scale Structure of Networks

a la Steyvers 2005

```{r, results='asis'}
network_properties <- tibble(
  names = map_chr(networks, ~ .x$name),
  vertices = map_int(networks, vcount),
  edges = map_dbl(networks, ecount) %>%
    as.integer(), # for some reason igraph ecount returns double
  avg_degree = map(networks, degree) %>%
    map_dbl(mean),
  avg_shortest_path = map_dbl(networks, mean_distance),
  diameter = map_dbl(networks, diameter) %>%
    as.integer(),
  clustering_coefficient = map_dbl(networks, transitivity),
  avg_shortest_path_random = 0, # either estimate or calculate values for random nets
  diameter_random = 0,
  clustering_coefficient_random = 0
)

network_properties # improve formatting
```

Degree Distribution
```{r}
assoc_degree <- tibble(k = 1:length(degree_distribution(assoc_network)),
                       p = degree_distribution(assoc_network))
feature_degree <- tibble(k = 1:length(degree_distribution(feature_network)),
                       p = degree_distribution(feature_network))

ggplot(data = assoc_degree, aes(x = k, y = p)) + geom_line()
ggplot(data = feature_degree, aes(x = k, y = p)) + geom_line()
```
